---
title: "Numerical Results"
output:
  pdf_document:
    includes:
      in_header: "preamble.tex"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r setup2, include=FALSE}
knitr::read_chunk("./code/result_reduce.R")
```

## Numerical Results

This is the RMarkdown file to reproduce the numerical results of the work 

> Rui Tuo, Shiyuan He, Arash Pourhabib, Yu Ding and Jianhua Z. Huang (2021+). A Reproducing Kernel Hilbert Space Approach to Functional Calibration of Computer Models.

This RMarkdown file runs on the cached RData files in the `./data` folder. Follow the instructions of the `readme.md` file to reproduce the cached RData files.

Table 1--4 correspond to the tables in the simulation section of the manuscript. 

```{r, results='asis', echo = FALSE}
str = '\\clearpage
\\begin{table}
	\\caption{Simulation 1 (Param-Exp model). Comparison of methods with the cheap
		code (CC). The mean (and SE) of the $L_2$-loss and of the width and average coverage rate
		(CR) for the level 90\\%, 95\\% and 99\\% confidence intervals.} 
	\\begin{tabular}{|c|c|c|cc|cc|cc|}
		\\hline
		\\multirow{2}{*}{Code} 
		&\\multirow{2}{*}{Method} & \\multirow{2}{*}{$L_2$-loss} & 
		\\multicolumn{2}{c|}{90\\%}
		& \\multicolumn{2}{c|}{95\\%}
		& \\multicolumn{2}{c|}{99\\%} \\\\
		& & & Width & CR & Width & CR & Width & CR\\\\
	\\hline CC'

writeLines(str)
```

```{r simu1, results='asis', echo = FALSE}
```

```{r, results='asis', echo = FALSE}
str = '
\\hline
\\end{tabular}	
\\end{table}
'

writeLines(str)
```


```{r, results='asis', echo = FALSE}
str = '
\\begin{table}
	\\caption{Simulation 2 (Param-Quad model). Comparison of methods with the cheap
		code (CC). The mean (and SE) of the $L_2$-loss and of the width and average coverage rate
		(CR) for the level 90\\%, 95\\% and 99\\% confidence intervals.} 
	\\begin{tabular}{|c|c|c|cc|cc|cc|}
		\\hline
		\\multirow{2}{*}{Code} 
		&\\multirow{2}{*}{Method} & \\multirow{2}{*}{$L_2$-loss} & 
		\\multicolumn{2}{c|}{90\\%}
		& \\multicolumn{2}{c|}{95\\%}
		& \\multicolumn{2}{c|}{99\\%} \\\\
		& & & Width & CR & Width & CR & Width & CR\\\\
	\\hline CC'

writeLines(str)
```

```{r simu2, results='asis', echo = FALSE}
```

```{r, results='asis', echo = FALSE}
str = '
\\hline
\\end{tabular}	
\\end{table}
'

writeLines(str)
```



```{r, results='asis', echo = FALSE}
str = '\\clearpage
\\begin{table}
	\\caption{Simulation 3. Comparison of methods with the cheap
		code (CC). The mean (and SE) of the $L_2$-loss and of the width and average coverage rate
		(CR) for the level 90\\%, 95\\% and 99\\% confidence intervals.} 
	\\begin{tabular}{|c|c|c|cc|cc|cc|}
		\\hline
		\\multirow{2}{*}{Code} 
		&\\multirow{2}{*}{Method} & \\multirow{2}{*}{$L_2$-loss} & 
		\\multicolumn{2}{c|}{90\\%}
		& \\multicolumn{2}{c|}{95\\%}
		& \\multicolumn{2}{c|}{99\\%} \\\\
		& & & Width & CR & Width & CR & Width & CR\\\\
	\\hline CC'

writeLines(str)
```

```{r simu3, results='asis', echo = FALSE}
```

```{r, results='asis', echo = FALSE}
str = '
\\hline
\\end{tabular}	
\\end{table}
'

writeLines(str)
```




```{r, results='asis', echo = FALSE}
str = '\\begin{table}
	\\caption{Simulation 4. Comparison of methods with the cheap
		code (CC). The mean (and SE) of the $L_2$-loss and of the width and average coverage rate
		(CR) for the level 90\\%, 95\\% and 99\\% confidence intervals.} 
	\\begin{tabular}{|c|c|c|cc|cc|cc|}
		\\hline
		\\multirow{2}{*}{Code} 
		&\\multirow{2}{*}{Method} & \\multirow{2}{*}{$L_2$-loss} & 
		\\multicolumn{2}{c|}{90\\%}
		& \\multicolumn{2}{c|}{95\\%}
		& \\multicolumn{2}{c|}{99\\%} \\\\
		& & & Width & CR & Width & CR & Width & CR\\\\
	\\hline CC'

writeLines(str)
```

```{r simu4, results='asis', echo = FALSE}
```

```{r, results='asis', echo = FALSE}
str = '
\\hline
\\end{tabular}	
\\end{table}
'

writeLines(str)
```



